Trauma treatment delay

### 2023-09-11 manuscriptlongversion.Rmd
Continuing on intro

Trauma is still a major cause of death around the world today, taking the lives of around 4,4 million people each year, almost 8% of all deaths [@World_Health_Organization_2021]. In the United States, trauma is the 4th leading cause of death among the general population and the leading cause for people between the ages of 1 and 44 [@AAST_2020]. It is also an important cause hospitalization and morbidity among all age groups, including seniors, and are responsible for an estimated 10% of all years lived with a disability globally. This has a significant burden on social and economic level, costing countries billions of US dollars each year in healthcare and lost productivity. [@connolly_woo_lampron_perry_2018] [@World_Health_Organization_2021].

>>>>

Trauma is and has long been a major cause of death around the world today, taking the lives of around 4,4 million people each year, almost 8% of all deaths [@World_Health_Organization_2021]. In the United States, trauma is the 4th leading cause of death among the general population and the leading cause for people between the ages of 1 and 44 [@AAST_2020]. It is also an important cause hospitalization and morbidity among all age groups, including seniors, and are responsible for an estimated 10% of all years lived with a disability globally. This has a significant burden on social and economic level, costing countries billions of US dollars each year in healthcare and lost productivity. [@connolly_woo_lampron_perry_2018] [@World_Health_Organization_2021].
